CrystalPlan: an Experiment Planning Tool for Crystallography

### 2010-12-17 docs/CrystalPlan_paper/paper.tex
Refs #182: Paper

From an initial data set, the data analysis program ISAW \cite{Tao2006} is used
to calculate the the sample mounting orientation UB matrix, which is saved to a text file along with the lattice
parameters. CrystalPlan can load this UB matrix file and will use that UB matrix
in coverage calculations.

>>>>

From an initial data set, the data analysis program ISAW \cite{Mikkelson05} is used
to calculate the the sample mounting orientation UB matrix, which is saved to a text file along with the lattice
parameters. CrystalPlan can load this UB matrix file and will use that UB matrix
in coverage calculations.
